\Title

### 2015-10-13 moho-inversion.tex
Talk ab problems with A in Bott's method section

The computation and storage of the dense matrix $\mbf{A}$ is time consuming
and is often times the bottleneck of an inversion algorithm.
In practice, the derivative in \eq{jacobian} is often calculated through a
first-order finite-difference approximation.
Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
Forward modeling using tesseroids requires several trigonometric function
evaluations and numerical integration.
\todo{Cite forward modeling paper}
Both factors contribute significantly to the total computation time required to
evaluate $\mbf{A}$.

@@

\citet{bott_use_1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The method discretizes the basement relief into an equal grid of $N_x \times
N_y$ elements.
The method starts with an initial estimate of the basement relief
$\mbf{p}^0$ equal to the null vector and updates the estimate using the formula

@@

\citet{silva_fast_2014} showed that Bott's method can be formulated as
the Gauss-Newton method (\eq{gaussnewton})
by setting the Jacobian matrix to

@@

\noindent
in which $\mbf{I}$ is the identity matrix.
In this framework, Bott's method uses a Bouguer plate approximation to
linearize the Jacobian matrix.
Bott's method maintains the non-linearity of the predicted data
$\mbf{d}(\mbf{p}^k)$.

Bott's method can also be formulated as the Steepest Descent method
(\eq{steepest}) by setting the Jacobian matrix to

@@

Bott as Gauss-Newton.
Jacobian is diagonal.
Approximate the Jacobian by making tesseroid size tend to infinity to get
Bouguer slab.
This approximation is good for tesseroids because each will cover a large
enough area.
Show case for the Steepest Descent.
Extend the Jacobian to include lateral density variation.
Important because density-contrast is positive or negative depending if the
Moho is above or below the reference level.
Enforce that the use of a particular

>>>>

@@

\citet{bott_use_1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The basement relief is then discretized into an equal grid of $M_x \times
M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
Bott's iterative method starts with an initial estimate of the basement relief
$\mbf{p}^0$ equal to the null vector and updates the estimate using the formula

@@

\citet{silva_fast_2014} showed that Bott's method can be formulated as
a special case of the Gauss-Newton method (\eq{gaussnewton})
by setting the Jacobian matrix (\eq{jacobian}) to

@@

\noindent
in which $\mbf{I}$ is the identity matrix.
In this framework,
Bott's method uses a Bouguer plate approximation of the relief to
linearize the Jacobian matrix.
However, the non-linearity of the predicted data $\mbf{d}(\mbf{p}^k)$ is
preserved.

We propose that Bott's method can also be formulated as a special case of the
Steepest Descent method (\eq{steepest}) by setting the Jacobian matrix to

@@

One of the advantages of Bott's method over the traditional Gauss-Newton or
Steepest Descent is eliminating the computation and storage of the dense
Jacobian matrix $\mbf{A}$.
In practice, the derivatives in \eq{jacobian} are often calculated through a
first-order finite-difference approximation.
Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
Bott's method also does not require the solution of equation systems.

A disadvantage of Bott's method is that it suffers from instability
\citep{silva_fast_2014}.
A common approach to solve this issue is to apply a smoothing filter, like a
moving average, to the unstable estimate.

\subsection{Regularized Bott's method in spherical coordinates}

Approximate the Jacobian by making tesseroid size tend to infinity to get
Bouguer slab.
This approximation is good for tesseroids because each will cover a large
enough area.
Show case for the Steepest Descent.
Extend the Jacobian to include lateral density variation.
Important because density-contrast is positive or negative depending if the
Moho is above or below the reference level.
Enforce that the use of a particular
